Ms 1

### 2018-01-09 ms1/ms1_display.Rmd
panels for figure 1

claims_by_abx %>%
  filter(abx %in% c('pde', 'pde_approp', 'pde_inapprop', 'pde_nodx')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 1400), breaks=c(0, 250, 500, 750, 1000, 1250, 1400)) +
  coord_fixed(ratio=4/1400*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, all abx')

claims_by_abx %>%
  filter(abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'tmpsmx', 'levofloxacin')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 250), breaks=c(0, 50, 100, 150, 200, 250)) +
  coord_fixed(ratio=4/250*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, top 5')

claims_by_abx %>%
  filter(abx %in% c('amoxclav', 'doxycycline', 'nitrofurantoin', 'clindamycin')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 100), breaks=c(0, 50, 100)) +
  coord_fixed(ratio=4/100*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, next 5')
```

@@

abx_trends %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('n_pde', 'n_pde_approp', 'n_pde_inapprop', 'n_pde_nodx'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

>>>>

dummy = data_frame(
  year = rep(c(2011, 2014), 3),
  cpkp = c(0, 1500, 0, 250, 0, 100),
  panel = factor(c(1, 1, 2, 2, 3, 3)),
  abx = 'pde'
)

panel_labels = c('1'='a) Overall antibiotic consumption',
                 '2'='b) Top 6 most-used antibiotics',
                 '3'='c) Next 4 most-used antibiotics')

claims_by_abx %>%
  mutate(panel = factor(case_when(
    .$abx %in% c('pde', 'pde_approp', 'pde_inapprop', 'pde_nodx') ~ 1,
    .$abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'tmpsmx', 'levofloxacin') ~ 2,
    .$abx %in% c('amoxclav', 'doxycycline', 'nitrofurantoin', 'clindamycin') ~ 3
  ))) %>%
  mutate(abx=case_when(
    .$abx == 'pde' ~ 'Overall use',
    .$abx == 'pde_inapprop' ~ 'Inappropriate use',
    .$abx == 'pde_approp' ~ 'Appropriate use',
    .$abx == 'pde_nodx' ~ 'Indeterminate use',
    .$abx == 'amoxclav' ~ 'amox/clav',
    .$abx == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$abx)
  ) %>%
  arrange(year, desc(cpkp)) %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=dummy) +
  geom_line() +
  geom_text_repel(
    data=filter(., year==2013),
    aes(label=abx)
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank()) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

ggsave('fig/raw_drug.pdf', height=5.0, width=9.0, unit='in')
```

@@

abx_trends %>%
  mutate(antibiotic=case_when(
    .$antibiotic == 'n_pde' ~ 'Overall use',
    .$antibiotic == 'n_pde_inapprop' ~ 'Inappropriate use',
    .$antibiotic == 'n_pde_approp' ~ 'Appropriate use',
    .$antibiotic == 'n_pde_nodx' ~ 'Indeterminate use',
    .$antibiotic == 'amoxclav' ~ 'amox/clav',
    .$antibiotic == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$antibiotic)
  ) %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('Overall use', 'Inappropriate use', 'Appropriate use', 'Indeterminate use'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in claims per beneficiary per year from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 33), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=12),
        axis.text = element_text(size=12))

ggsave('fig/abx_trends.pdf', width=6.4, height=4.5, units='in')
```
